### 2021-01-08 Modules/Spatial_IIR-MathDerivations_EXT.tex
Before implementing Tsvi's comments

Time domain analysis of the proposed feedback based architecture, considering both propagation delay and attenuation, gives rise to
\begin{equation}
    \label{eqn:SingleSensorTemporalEquality}
    % \resizebox{.91\linewidth}{!}{
        \begin{split}
            x_{n}(t) = g\rBrace{s\rBrace{t-\tau_{pd}-\tau_{n}}
            +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{t-\tau_{pd}-\tau_{n}}}},
        \end{split}
    % }
\end{equation}
where the first term on the right-hand-side (RHS) represents the contribution of the transmitted waveform $s(t)$ to the $n$'th array element and the second term represents the feedback contribution of the re-transmitted array signal to this same element.
Expressing the Fourier transform of \eqref{eqn:SingleSensorTemporalEquality},
\begin{equation}
    \label{eqn_singleSensorFourier}
    % \resizebox{.91\linewidth}{!}{
        \begin{split}
            X_{n} =
            g\Bigg( & \F{s}
            \exp\rBrace{-j\omega\rBrace{\tau_{pd}+\tau_{n}}}
            \\&+\sum_{m=0}^{N-1}
            {
            \alpha^{*}_{m}\omegaB\F{x}_{m}
            \exp\rBrace{-j\omega\rBrace{\tau_{pd}+\tau_{n}}}
            }\Bigg),
        \end{split}
    % }
\end{equation}
and its vector from,
$$
\F{\vx} = g\rBrace{\F{s}+\vAlphaH \F{\vx}}\vd\exp{\rBrace{-j\omega\tau\_{pd}}},
$$
we find that it can be simplified to
$$
\F{\vx} =g\rBrace{I-g\vd\vAlphaH{}e^{-j\omega\tau_{pd}}}^{-1}\vd\F{s}\exp{\rBrace{-j\omega\tau_{pd}}}.
$$
Then, denoting
\[
\phi\triangleq\omega\tau_{pd}
\]
as the round-trip signal propagation related electrical phase and using the Woodbury matrix identity \cite{woodbury1950inverting}, we find that
$$
\F{\vx}
=
\frac{    
g\vd\exp{\rBrace{-j\phi}}
}{
1 - g\aHd{}\exp{\rBrace{-j\phi}}
}\F{s}.
$$
Let $z=\vBetaH{}\vecnot{x}+\text{n}$ be the beamformer's output (see Fig.~\ref{fig:Proposed_spatialIIR_ARCH}), with Fourier transform $Z$. Considering the noiseless case $\rBrace{\text{i.e., n}=0}$, the frequency response of the FB is 
\begin{equation}
\label{eqn:GeneralFeedbackTransferFunction}
\Hba
\triangleq
\frac{\F{z}}{\F{s}} 
=
\frac{    
g\bHd{}\exp\rBrace{-j\phi}
}{
1 - g\aHd{}\exp\rBrace{-j\phi}
}.
\end{equation}
\par Note that this architecture achieves a controllable (via setting of $\vBeta$ and $\vAlpha$) and recursive (non-trivial denominator) spatial response.
As will be shown, high directivity and narrow beamwidth are obtainable by proper selection of the weights. Compared to traditional beamformers (i.e., without feedback), the performance improvement will be expressed in terms of increased aperture, narrower beamwidth and improved sidelobe attenuation.
One may observe that opposed to traditional beamformers, the array response, $\Hba,$ is not only influenced by the impinging signal DOA, for it is also range selective due to its $\phi$ dependency.
As demonstrated in Fig.~\ref{fig_rangeAzimuthSelectivity}, the combination of both angular and range selectivity enables the designer to enhance signals arriving from specific locations (grey area) rather than only specific directions.
\begin{figure}[t!]
    \begin{center}
        \begin{overpic}[width=0.65\linewidth, 
        % grid, 
        tics=10,trim=0 0 0 0]{./Media/azimuthRangSelectivity.png}
            \put (20, 23){\rotatebox{0}{\footnotesize{Angular response}}}
            \put (30.5, 47){\rotatebox{0}{\footnotesize{Enhanced radial slice}}}
        \end{overpic}
    \end{center}
    \caption{
    % A visualization of the spatial area selectivity concept.
    Combining both radial selectivity and DOA-based selectivity allows to localize the transmitter.
    }
    \label{fig_rangeAzimuthSelectivity}
\end{figure}

>>>>

Time domain analysis of the proposed feedback based architecture, considering both propagation delay and attenuation, gives rise to
\begin{equation}
    \label{eqn:SingleSensorTemporalEquality}
    % \resizebox{.91\linewidth}{!}{
        \begin{split}
            x_{n}(t) = g\rBrace{s\rBrace{t-\tau_{pd}-\tau_{n}}
            +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{t-\tau_{pd}-\tau_{n}}}},
        \end{split}
    % }
\end{equation}
where the first term on the right-hand-side (RHS) represents the contribution of the transmitted waveform $s(t)$ to the $n$'th array element and the second term represents the feedback contribution of the re-transmitted array signal to this same element.
Expressing the Fourier transform of \eqref{eqn:SingleSensorTemporalEquality},
\begin{equation}
    \label{eqn_singleSensorFourier}
    % \resizebox{.91\linewidth}{!}{
        \begin{split}
            X_{n} =
            g\Bigg( & \F{s}
            \exp\rBrace{-j\omega\rBrace{\tau_{pd}+\tau_{n}}}
            \\&+\sum_{m=0}^{N-1}
            {
            \alpha^{*}_{m}\F{x}_{m}
            \exp\rBrace{-j\omega\rBrace{\tau_{pd}+\tau_{n}}}
            }\Bigg),
        \end{split}
    % }
\end{equation}
and its vector from,
$$
\F{\vx} = g\rBrace{\F{s}+\vAlphaH \F{\vx}}\vd\exp{\rBrace{-j\omega\tau_{pd}}},
$$
we find that it can be simplified to
$$
\F{\vx} =g\rBrace{I-g\vd\vAlphaH{}e^{-j\omega\tau_{pd}}}^{-1}\vd\F{s}\exp{\rBrace{-j\omega\tau_{pd}}}.
$$
Then, denoting
\[
\phi\triangleq\omega\tau_{pd}
\]
as the round-trip signal propagation related electrical phase and using the Woodbury matrix identity \cite{woodbury1950inverting}, we find that
$$
\F{\vx}
=
\frac{    
g\vd\exp{\rBrace{-j\phi}}
}{
1 - g\aHd{}\exp{\rBrace{-j\phi}}
}\F{s}.
$$
Let $z=\vBetaH{}\vecnot{x}+\text{n}$ be the beamformer's output (see Fig.~\ref{fig:Proposed_spatialIIR_ARCH}), with Fourier transform $Z$. Considering the noiseless case $\rBrace{\text{i.e., n}=0}$, the frequency response of the FB is 
\begin{equation}
\label{eqn:GeneralFeedbackTransferFunction}
\Hba
\triangleq
\frac{\F{z}}{\F{s}} 
=
\frac{    
g\bHd{}\exp\rBrace{-j\phi}
}{
1 - g\aHd{}\exp\rBrace{-j\phi}
}.
\end{equation}
\par Note that this architecture achieves a controllable (via setting of $\vBeta$ and $\vAlpha$) and recursive (non-trivial denominator) spatial response.
As will be shown, high directivity and narrow beamwidth are obtainable by a proper selection of the weights. Compared to traditional beamformers (i.e., without feedback), the performance improvement will be expressed in terms of increased aperture, narrower beamwidth and improved sidelobe attenuation.
One may observe that opposed to traditional beamformers, the array response, $\Hba,$ is not only influenced by the impinging signal DOA, since it is also range selective due to its $\phi$ dependency.
As demonstrated in Fig.~\ref{fig_rangeAzimuthSelectivity}, the combination of both angular and range selectivity enables the designer to enhance signals arriving from specific locations (grey area) rather than only specific directions.
\begin{figure}[t!]
    \begin{center}
        \begin{overpic}[width=0.75\linewidth, 
        % grid, 
        tics=10,trim=0 0 0 0]{./Media/azimuthRangSelectivity.png}
            \put (20, 23){\rotatebox{0}{\footnotesize{Angular response}}}
            \put (32, 47){\rotatebox{0}{\footnotesize{Enhanced radial slice}}}
        \end{overpic}
    \end{center}
    \caption{
    % A visualization of the spatial area selectivity concept.
    Combining both radial selectivity and DOA-based selectivity allows to localize the transmitter.
    }
    \label{fig_rangeAzimuthSelectivity}
\end{figure}

### 2021-01-08 Modules/sec_rangeSensitivityError_EXT.tex
Before implementing Tsvi's comments

In this section, we investigate $\HrTPr$ for the general case, where also range misalignment phase term $\dPhi$ is possibly non zero. In Fig.~\ref{fig_hDUDTContour}, we plot $\abs{\HrTPr}$ in logarithmic scale, with respect to both steer and range misalignments.

@@

First, we notice that although setting $r\to1$ (i.e., close to perfect gain match), sharpens the beampattern's main lobe  (i.e., higher spatial selectivity), it also amplifies the range error ($\dPhi$) related sensitivity as the main lobe's support over the $\dPhi/\pi$ axis shrinks. 

@@

where $R_{\text{rt}}=2R$ is the round-trip distance between the array and the target of interest. 

@@

\Delta R_{\text{rt}}\omegaB=\frac{\dPhi\lambda}{2\pi} 

@@

Figure~\ref{fig_rangError} shows that even minor range errors of $\Delta R_{\text{rt}}\sim0.1\lambda$ significantly distort the beampattern.

>>>>

In this section, we investigate $\HrTPr$ for the general case, where the range misalignment phase term $\dPhi$ may also be non zero. In Fig.~\ref{fig_hDUDTContour}, we plot $\abs{\HrTPr}$ in logarithmic scale, with respect to both steer and range misalignments.

@@

First, we notice that although setting $r\to1$ (i.e., close to a perfect gain match), sharpens the beampattern's main lobe  (i.e., higher spatial selectivity), it also amplifies the range error ($\dPhi$) related sensitivity as the main lobe's support over the $\dPhi/\pi$ axis shrinks. 

@@

where $R_{\text{rt}}=2R$ is the round-trip distance between the array and the target of interest and $\lambda$ is the wavelength. 

@@

\Delta R_{\text{rt}}=\frac{\dPhi\lambda}{2\pi} 

@@

Fig.~\ref{fig_rangError} shows that even minor range errors of $\Delta R_{\text{rt}}\sim0.1\lambda$ significantly distort the beampattern.

### 2021-01-08 Modules/stabilityEnhancement_freqPairApproach_EXT.tex
Before implementing Tsvi's comments

\subsection*{Suggested processing scheme}
\begin{figure}[t!]
    \begin{center}
        \begin{overpic}[width=0.9\linewidth, 
        % grid, 
        tics=10,trim={0 0 0 0}]{./Media/SpatialIIR_APP.png}
            \put (12.5, 64){$\text{FB}_{\vAlphaI{1},\vBetaI{1}}$}
            \put (61, 64){$\text{FB}_{\vAlphaI{2},\vBetaI{2}}$}
            \put (4.5, 59){$z_{1}\rBrace{t}$}
            \put (54, 59){$z_{2}\rBrace{t}$}
            \put (12.9, 41.5){$\text{BPF}_{\omega_{1}}$}
            \put (61.65, 41.5){$\text{BPF}_{\omega_{2}}$}
            \put (6, 51.5){+}
            \put (55, 51.5){+}
            \put (16, 51.5){\footnotesize{$\text{n}_{1}\rBrace{t}$}}
            \put (64.75, 51.5){\footnotesize{$\text{n}_{2}\rBrace{t}$}}
            \put (24.5, 59){\footnotesize{$\Tx_{1}\rBrace{t}$}}
            \put (73.5, 59){\footnotesize{$\Tx_{2}\rBrace{t}$}}
            \put (36.25, 64){\scriptsize{$s_{1}\rBrace{t}$}}
            \put (43, 64){\scriptsize{$s_{2}\rBrace{t}$}}
            \put (18.25, 13){\footnotesize{Harmonic mean}}
            \put (32, 2){$Z_{\text{DF}}$}
            \put (54.75, 24){$\Sigma$}
            \put (21.75, 25){\footnotesize{$\mathcal{F}_{\omega_{1}}$}}
            \put (30.75, 25){\footnotesize{$\mathcal{F}_{\omega_{2}}$}}
        \end{overpic}
    \end{center}
    \caption{Dual-frequency beamformer, consisting of two independent FB blocks and narrowband bandpass filters. The blocks marked by $\mathcal{F}_{\omega_{i}}$ compute the Fourier coefficients in $\omega_{i}$ and their outputs feed the harmonic mean calculator, which generates the DF beamformer's output.}
    \label{fig_app}
\end{figure}
In Fig.~\ref{fig_app}, we demonstrate the use of two independently configured FB instances (see also Fig.~\ref{fig:Proposed_spatialIIR_ARCH}), where each instance is designed to treat a specific frequency band.
A bandpass filter $\text{BPF}_{\omega_{i}},\;i=1,2$ filters a narrowband slice around $\omega_{i}=2\pi f_i$. These filters are used to generate both the transmitted feedback signal ($\text{Tx}_{i}$) and the outputs $z_{i}$. 
The inputs $s_{i}(t) = \exp\Brack{j\omega_{i}t}$  are the two narrowband stimuli signals and $\text{n}_{i}(t)$ describe the additive noise.

Note that in the suggested architecture we do not add array elements, but merely double the beamformer processing effort. 
\par For each FB block, its output is given by
\[
z_{i}(t)=H_{\vBetaI{i},\vAlphaI{i}}\rBrace{\omega_{i}}\exp{\rBrace{j\omega_{i}t}}\ \ {i\in\cBrace{1,2}},
\]
where $\vBetaI{i},\vAlphaI{i}$ are the coefficients of the $i$'th beamformer.
Motivated by the desire to mitigate the $\Delta\phi$ dependency of the system, which appears in the denominator of \eqref{eq_generalH}, we compute the reciprocal of each frequency response, average, and compute the reciprocal again. This leads to the harmonic mean of both beamformers' outputs (see Fig.~\ref{fig_app}), which formally, up to a constant term, takes the form
\begin{equation}
    \label{eqn_HDF_def}
    Z_{\text{DF}} = \abs{H^{-1}_{\vBetaI{1}\vAlphaI{1}}\rBrace{\omega_{1}}+H^{-1}_{\vBetaI{2},\vAlphaI{2}}\rBrace{\omega_{2}}}^{-1}.
\end{equation}
% Note that, as in IIR filters, the system stabilizes after a certain period, therefore the Fourier weights should be calculated after stabilization.
% As a rule of thumb, simulations show that the stabilization period is around $100R/c$. 
\ifdefined\useOmega
Straight forward derivations, Allowing $g$ to be frequency dependent, leads to
\else
For convenience, we use subscripts instead of formal $\omega$ dependency such that $\phiI{i}\triangleq\phi\rBrace{\omega_{i}}, \gI{i}\triangleq{}g\rBrace{\omega_{i}}, \vdI{i}\triangleq\vecnot{d}\rBrace{\omega_{i}}$.
Also, $r_i\triangleq{}\gI{i}/\gIHat{i}$ is denoted to be the gain mismatch at $\omega_i$.

@@

\begin{proof}
See App.~\ref{apdx_thrm_DF}. 
\end{proof}
\par Assuming close frequencies, $Z_{\text{DF}}$ in  \eqref{eqn_H_DF_general} closely resembles the single frequency (SF) beampattern in  \eqref{eqn:GeneralFeedbackTransferFunction}, where the range related phase $\phi$ is now replaced by  $\phiI{1}-\phiI{2}=(\omega_1-\omega_2)\tau_{pd}$. 
Hence, one may significantly mitigate the range mismatch distortion of the beampattern by selecting close stimuli frequencies.
% Also, $\tau_n$ is arbitrary, hence the discussion is not restricted to a specific array geometry.
We also note that throughout the development of \eqref{eqn_H_DF_general}, we did not assume any specific array geometry, hence this result is valid for arbitrary arrays and not just ULA.
\subsection*{Numerical example}
Consider a radio frequency carrier of $10$~GHz and typical range error of $\Delta{}R_{\text{rt}}=10$~m, which is $333\frac{1}{3}\lambda$ (assuming  speed of light, $c=3\cdot 10^{8}$~m/s). The single frequency beampattern distortion, being periodic in $\lambda$, will closely resemble the $0.3\lambda$ error plot presented in Fig.~\ref{fig_rangError}. Assume that we aim to achieve a maximal phase error of $\Delta \phi=0.01\pi$. Hence, when using DF architecture, the dictated frequency separation must satisfy
\begin{equation}\label{eq_DF_phErr}
\abs{(\omega_1-\omega_2)\frac{\Delta{}R_{\text{rt}}}{c}}<0.01\pi.
\end{equation}
or equivalently, for maximal range error of $10$~m, a frequency separation of
\[
\abs{f_1-f_2}<0.005 c/\Delta{}R_{\text{rt}}=150 \,\text{kHz}
\]
is required.

@@

\par Simulating the DF architecture, configured to mitigate range estimation errors as in \eqref{eq_DF_phErr} and plotting its normalized (to $0$~dB peak gain) beampattern together with the perfectly range aligned scenario, we show in Fig.~\ref{fig_dualfreq_rangeErrorHighSnr} that the DF architecture achieves near-optimal performance, despite the inherent range error of $\Delta{}R_{\text{rt}}=10$~m.
In Fig.~\ref{fig_dualfreq_perfectAlignLowSnr}, we repeat the simulation while adding white Gaussian noise to the output of each feedback beamformer. Evidently, even in the noisy case, the DF beamformer achieves close-to-ideal beampattern, while the SF beamformer suffers severe distortions.

@@

    \caption{Simulating the 3 element ULA with $r_1=0.6^{2},\; r_2=0.6$ (hence $\kappa=0.6$), assuming an infinite SNR. For each target direction $\thetaD$, the DF beamformer output $Z_\text{DF}$ is evaluated where the beamformer is set to enhance signals impinging from $\thetaD=\pi/2$. 

@@

        \begin{overpic}[width=.9\linewidth, 

>>>>

\subsection*{Suggested processing scheme}
\begin{figure}[t!]
    \begin{center}
        \begin{overpic}[width=0.99\linewidth, 
        % grid, 
        tics=10,trim={0 0 0 0}]{./Media/SpatialIIR_APP.png}
            \put (12.5, 64){$\text{FB}_{\vAlphaI{1},\vBetaI{1}}$}
            \put (61, 64){$\text{FB}_{\vAlphaI{2},\vBetaI{2}}$}
            \put (4.5, 59){$z_{1}\rBrace{t}$}
            \put (54, 59){$z_{2}\rBrace{t}$}
            \put (12.9, 41.5){$\text{BPF}_{\omega_{1}}$}
            \put (61.65, 41.5){$\text{BPF}_{\omega_{2}}$}
            \put (6, 51.5){+}
            \put (55, 51.5){+}
            \put (16, 51.5){\footnotesize{$\text{n}_{1}\rBrace{t}$}}
            \put (64.75, 51.5){\footnotesize{$\text{n}_{2}\rBrace{t}$}}
            \put (24.5, 59){\footnotesize{$\Tx_{1}\rBrace{t}$}}
            \put (73.5, 59){\footnotesize{$\Tx_{2}\rBrace{t}$}}
            \put (36.25, 64){\scriptsize{$s_{1}\rBrace{t}$}}
            \put (43, 64){\scriptsize{$s_{2}\rBrace{t}$}}
            \put (18.75, 13){\footnotesize{Harmonic mean}}
            \put (32, 2){$Z_{\text{DF}}$}
            \put (54.75, 24){$\Sigma$}
            \put (22, 25){\footnotesize{$\mathcal{F}_{\omega_{1}}$}}
            \put (30.75, 25){\footnotesize{$\mathcal{F}_{\omega_{2}}$}}
        \end{overpic}
    \end{center}
    \caption{Dual-frequency beamformer, consisting of two independent FB blocks and narrowband bandpass filters. The blocks marked by $\mathcal{F}_{\omega_{i}}$ compute the Fourier coefficients in $\omega_{i}$ and their outputs feed the harmonic mean calculator, which generates the DF beamformer's output.}
    \label{fig_app}
\end{figure}
In Fig.~\ref{fig_app}, we demonstrate the use of two independently configured FB instances (see also Fig.~\ref{fig:Proposed_spatialIIR_ARCH}), where each instance is designed to treat a specific frequency band.
A bandpass filter $\text{BPF}_{\omega_{i}},\;i=1,2$ filters a narrowband slice around $\omega_{i}=2\pi f_i$. These filters are used to generate both the transmitted feedback signal ($\text{Tx}_{i}$) and the outputs $z_{i}$. 
The inputs $s_{i}(t) = \exp\Brack{j\omega_{i}t}$  are the two narrowband stimuli signals and $\text{n}_{i}(t)$ represents the additive noise.

Note that in the suggested architecture we do not add array elements, but merely double the beamformer processing effort. 
\par For each FB block, its output is given by
\[
z_{i}(t)=H_{\vBetaI{i},\vAlphaI{i}}\rBrace{\omega_{i}}\exp{\rBrace{j\omega_{i}t}}\ \ {i\in\cBrace{1,2}},
\]
where $\vBetaI{i},\vAlphaI{i}$ are the coefficients of the $i$'th beamformer.
Motivated by the desire to mitigate the $\Delta\phi$ dependency of the system, which appears in the denominator of \eqref{eq_generalH}'s RHS, we compute the reciprocal of each frequency response, average, and compute the reciprocal again. This leads to the harmonic mean of both beamformers' outputs (see Fig.~\ref{fig_app}), which formally, up to a constant term, takes the form
\begin{equation}
    \label{eqn_HDF_def}
    Z_{\text{DF}} = \abs{H^{-1}_{\vBetaI{1}\vAlphaI{1}}\rBrace{\omega_{1}}+H^{-1}_{\vBetaI{2},\vAlphaI{2}}\rBrace{\omega_{2}}}^{-1}.
\end{equation}
% Note that, as in IIR filters, the system stabilizes after a certain period, therefore the Fourier weights should be calculated after stabilization.
% As a rule of thumb, simulations show that the stabilization period is around $100R/c$. 
For convenience, we use subscripts instead of formal $\omega$ dependency such that $\phiI{i}\triangleq\phi\rBrace{\omega_{i}}, \gI{i}\triangleq{}g\rBrace{\omega_{i}}, \vdI{i}\triangleq\vecnot{d}\rBrace{\omega_{i}}$.
Also, $r_i\triangleq{}\gI{i}/\gIHat{i}$ is denoted to be the gain mismatch at $\omega_i$.

@@

\begin{proof}
See App.~\ref{apdx_thrm_DF}. 
\end{proof}
\par Assuming close frequencies, $Z_{\text{DF}}$ in  \eqref{eqn_H_DF_general} closely resembles the single frequency (SF) beampattern in  \eqref{eqn:GeneralFeedbackTransferFunction}, where the range related phase $\phi$ is now replaced by  $\phiI{1}-\phiI{2}=(\omega_1-\omega_2)\tau_{pd}$. 
Hence, one may significantly mitigate the range mismatch distortion of the beampattern by selecting close stimuli frequencies.
% Also, $\tau_n$ is arbitrary, hence the discussion is not restricted to a specific array geometry.
We also note that throughout the development of \eqref{eqn_H_DF_general}, we did not assume any specific array geometry, hence this result is valid for arbitrary arrays and not just ULA.
\subsection*{Numerical example}
Consider a radio frequency carrier of $10$~GHz and typical range error of $\Delta{}R_{\text{rt}}=10$~m, which is $333\frac{1}{3}\lambda$ (assuming  speed of light, $c=3\cdot 10^{8}$~m/s). The single frequency beampattern distortion, being periodic in $\lambda$, will closely resemble the $0.3\lambda$ error plot presented in Fig.~\ref{fig_rangError}. Assume that we aim to achieve a maximal phase error of $\Delta \phi=0.01\pi$. Hence, when using the DF architecture, the dictated frequency separation must satisfy
\begin{equation}\label{eq_DF_phErr}
\abs{(\omega_1-\omega_2)\frac{\Delta{}R_{\text{rt}}}{c}}<0.01\pi.
\end{equation}
or equivalently, for a maximal range error of $10$~m, a frequency separation of
\[
\abs{f_1-f_2}<0.005 c/\Delta{}R_{\text{rt}}=150 \,\text{kHz}
\]
is required.

@@

\par Simulating the DF architecture, configured to mitigate range estimation errors as in \eqref{eq_DF_phErr} and plotting its normalized (to $0$~dB peak gain) beampattern together with the perfectly range aligned scenario, we show in Fig.~\ref{fig_dualfreq_rangeErrorHighSnr} that the DF architecture achieves a near-optimal performance, despite the inherent range error of $\Delta{}R_{\text{rt}}=10$~m.
In Fig.~\ref{fig_dualfreq_perfectAlignLowSnr}, we repeat the simulation while adding white Gaussian noise to the output of each feedback beamformer. Evidently, even in the noisy case, the DF beamformer achieves a close-to-ideal beampattern, while the SF beamformer suffers from severe distortions.

@@

    \caption{Simulating a 3 element ULA with $r_1=0.6^{2},\; r_2=0.6$ (hence $\kappa=0.6$), assuming an infinite SNR. For each target direction $\thetaD$, the DF beamformer output $Z_\text{DF}$ is evaluated where the beamformer is set to enhance signals impinging from $\thetaD=\pi/2$. 

@@

        \begin{overpic}[width=.99\linewidth, 

### 2021-01-08 main/intro.tex
Before implementing Tsvi's comments

\par
TODO: Elaborate on the 2/3D planar from (by order)
\begin{itemize}
    \item Highly Selective Three-Dimensional Recursive Beam Filters Using Intersecting Resonant Planes 
    \item Three-Dimensional Cone Filter Banks
    \item A Speed-Optimized Systolic Array ProcessorArchitecture for Spatio-Temporal 2-D IIRBroadband Beam Filters
    \item UWB Beamforming Using 2-D Beam Digital Filters
\end{itemize}

>>>>

% \par
% TODO: Elaborate on the 2/3D planar from (by order)
% \begin{itemize}
%     \item Highly Selective Three-Dimensional Recursive Beam Filters Using Intersecting Resonant Planes 
%     \item Three-Dimensional Cone Filter Banks
%     \item A Speed-Optimized Systolic Array ProcessorArchitecture for Spatio-Temporal 2-D IIRBroadband Beam Filters
%     \item UWB Beamforming Using 2-D Beam Digital Filters
% \end{itemize}
